---
title: "Data Wrangling Exercise 1: Basic Data Manipulation"
author: "Clayton Glasser"
date: "June 21, 2018"
output: html_document
---

# 1
Load tidyverse and store the csv data into a dataframe called titanic. 

```{r}
library(tidyverse)
titanic <- read_csv("titanic_original.csv")

titanic
```

# 2
* Store "s" in any occurance of NA inside the `embark` column then
* Calculate the mean of all the entries in the `age` column, excluding any missing values, and store it in `mean_age` then
* Store `mean_age` in any occurance of NA inside the `age` column then
* Store "none" in any instance which is NA inside the `boat` column then
* If instance of `titanic$cabin` is NaN set it equal numeric 0, else numeric 1, assign it to new column: `has_cabin_number`, add new column to dataframe `titanic`, and store new new `titanic` in original `titanic`. 

```{r}
titanic$embarked[is.na(titanic$embarked)] <- "s"
mean_age <- mean(titanic$age, na.rm = TRUE)
titanic$age[is.na(titanic$age)] <- mean_age
titanic$boat[is.na(titanic$boat)] <- "none"
titanic <- titanic %>% mutate(has_cabin_number = ifelse(is.na(titanic$cabin), 0, 1))

```

# 3
End result:

```{r}
titanic
```